---
title: "Reverse Engineering Project"
author: "Student names here"
date: "Date here"
output:
  html_document:
    theme: cerulean
    highlight: pygments
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

In this notebook, we are reverse engineering the story, [STORY NAME](STORY%20URL)

## Load libraries

Loading required libraries for this analysis.

```{r echo=FALSE, message=FALSE}

library(tidyverse)
library(tidycensus)
library(janitor)
```

## Load and Cleaning Data

In this section, describe the source of the data, write a basic data dictionary for data you are working with, and discuss any caveats or issues you discovered working with this data.

```{r}
# Load required data

# Path to data should be loaded from folder "data" i.e. read_csv("data/name_of_data.csv")

# Clean required data and prepare for analysis if needed. 


game_reviews <- read_csv2("Data/bgg_dataset.csv")|> clean_names()


```

## Sentences to Engineer

In this notebook, we are reverse engineering five sentences from the story.

### Sentence 1

-   **Sentence text**: What years had games owned by the most users?
-   **Analysis summary**: [Write up two to three sentences describing the results of your analysis. Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

### Sentence 2

-   **Sentence text**: Comparing the average rating of board games between 1900-2000 and 2000-present.
-   **Analysis summary**: [Write up two to three sentences describing the results of your analysis. Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

### Sentence 3

-   **Sentence text**: Are singleplayer or multiplayer games more reviewed?
-   **Analysis summary**: Singleplayer games have fewer reviews than multiplayer games, as shown by the \# of Ratings column below. There are 168,000 more reviews for multiplayer games than singleplayer games. However, there is also a much larger number of multiplayer games overall when compared to singleplayer - there are less than 500 singleplayer games in the review list.

```{r}
# This code shows the number of reviews for games that are considered multiplayer (2 or more players) compared to those that are considered singleplayer (no more than 1 player)

game_reviews <- game_reviews |>
  #Code for singleplayer or multiplayer
  mutate(
    player_type = case_when(
      #This does not account for games where the maximum players is less than 0 because some have a min_players that is more than 1. 
     max_players == 1~ "Singleplayer",
     max_players >= 2 ~ "Multiplayer",
        .default = NA
      )
  )
#Group by player type and count the number of ratings. Also, a sum of the number of games considered multiplayer and singleplayer for context. 
game_reviews |> group_by(player_type)|>
  summarise("# of Ratings" = sum(users_rated), "# of Games" = n())
  

```

### Sentence 4

-   **Sentence text**: What is the average number of games by age group?
-   **Analysis summary**: [Write up two to three sentences describing the results of your analysis. Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

### Sentence 5

-   **Sentence text**: [Paste in sentence to engineer here]
-   **Analysis summary**: [Write up two to three sentences describing the results of your analysis. Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

-30-
