---
title: "Reverse Engineering Project"
author: "Student names here"
date: "Date here"
output:
  html_document:
    theme: cerulean
    highlight: pygments
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

In this notebook, we are reverse engineering the story, [STORY NAME](STORY%20URL)

## Load libraries

Loading required libraries for this analysis.

```{r echo=FALSE, message=FALSE}

library(tidyverse)
library(tidycensus)
library(janitor)
```

## Load and Cleaning Data

In this section, describe the source of the data, write a basic data dictionary for data you are working with, and discuss any caveats or issues you discovered working with this data.

```{r}
# Load required data

# Path to data should be loaded from folder "data" i.e. read_csv("data/name_of_data.csv")

# Clean required data and prepare for analysis if needed. 


game_reviews <- read_csv2("Data/bgg_dataset.csv")|> clean_names()


```

## Sentences to Engineer

In this notebook, we are reverse engineering five sentences from the story.

### Sentence 1

-   **Sentence text**: What years had games owned by the most users?
-   **Analysis summary**: [Write up two to three sentences describing the results of your analysis. Were you able to confirm the finding? If not, why not?]

```{r}
board_game_ages <- board_game_data |>
mutate(
age_groups = case_when(
between(min_age, 1, 5) ~ '1-5',
between(min_age, 6, 12) ~ '6-12',
between(min_age, 13, 17) ~ '13-17',
min_age >= 18 ~ '18+',
.default = 'N/A'
)
)

board_game_ages |>
group_by(age_groups) |>
summarise(
total_games = n()
) |>
filter(age_groups != 'N/A') |>
arrange(desc(total_games))

```

### Sentence 2

-   **Sentence text**: Comparing the average rating of board games between 1900-2000 and 2000-present.
-   **Analysis summary**: [Write up two to three sentences describing the results of your analysis. Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

### Sentence 3

-   **Sentence text**: Are singleplayer or multiplayer games more reviewed?
-   **Analysis summary**: Singleplayer games have fewer reviews than multiplayer games, as shown by the total ratings column below. There are about 168,000 more reviews for multiplayer games than singleplayer games. However, there is also a much larger number of multiplayer games overall when compared to singleplayer - there are less than 500 singleplayer games in the review list. This means that there are statistically more opportunities to review multiplayer games than singleplayer and, potentially, groups involved in playing multiplayer games may individually leave multiple reviews for those games, resulting in many more ratings for those games than singleplayers. We calculated an average number of ratings to account for this difference, showing multiplayer games on average have a higher number of ratings.

```{r}
# This code shows the number of reviews for games that are considered multiplayer (2 or more players) compared to those that are considered singleplayer (no more than 1 player)

game_reviews <- game_reviews |>
  #Creating a new column for total players that will determine if player count can not be more than 1.
  mutate(total_players = min_players + max_players)|>
  mutate(
    player_type = case_when(
      #Defining multiplayer as any game where total players can be more than 1. If a game is equal or fewer to 1 then it is singleplayer. 
    total_players >= 2 ~ "Multiplayer",
     total_players <= 1 ~ "Singleplayer",
        .default = NA
      )
  )
#Group by player type and count the number of ratings. Also, a sum of the number of games considered multiplayer and singleplayer for context. 
game_reviews |> group_by(player_type)|>
  summarise(total_ratings = sum(users_rated), total_games = n(), "Average Ratings" = total_ratings/total_games)
  

```

### Sentence 4

-   **Sentence text**: What years had the games owned by the most users?
-   **Analysis summary**: [Write up two to three sentences describing the results of your analysis. Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

### Sentence 5

-   **Sentence text**: What are the domains with the highest average ratings?
-   **Analysis summary**: [Write up two to three sentences describing the results of your analysis. Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

-30-
