---
title: "lab_09.Rmd"
author: "derek willis"
date: "2023-04-12"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## You will need

-   A Datawrapper account
-   Data in CSV files in the `data` folder

## Load libraries and establish settings

**Task** Create a codeblock and load appropriate packages and settings
for this lab.

```{r}
# load libraries here

library(tidyverse)
library(janitor)
```

## Questions

**Q1.** You want to explore the differences between the electoral
performances of Dan Cox in 2022 and Larry Hogan in 2018. Except a map is
probably not the best way to show that. Let's make a chart instead, and
the type is up to you, but the goal is to clearly show the differences
between the two.

You MUST do the following things when answering this question:

\* Load the md_gov_county.csv and md_gov_county_18.csv files from the
data folder

\* Join those dataframes, specifying the join column.

\* Add columns to generate percentages for Cox and Hogan.

\* Export that joined dataframe to a CSV file using `write_csv`.

\* Using that exported CSV, make a chart with Datawrapper. What kind of
chart is up to you, so experiment with a few kinds of charts to see what
answers the question above in the clearest way.

Your chart MUST: \* Have a title, description and source that tells
readers about the data. The title and description should highlight the
most newsworthy or important aspect. \* Easily readable labels and
values \* Publish your chart \* Describe your thought process below -
why you chose to make the chart you did - and add the URL of your chart.

<https://www.datawrapper.de/_/j7Mk4/>

I chose a Scatterplot because it was the clearest way to highlight a
comparison of Cox and Hogan without knowing how to filter the columns in
Datawrapper to only Cox and Hogan's percentages. This way, there is a
point showing the county and following the X axis will show the percent
of votes that Cox had compared to that of Hogan's. I think this is an
easy way to follow the percentages in a comparison without seeing too
many bars or lines.

**A1.**

```{r}
#Load datasets
md_gov_county <- read_csv("data/md_gov_county.csv")
md_gov_18 <- read_csv("data/md_gov_county_18.csv")

#Join Dataframes
md_cands_18_22 <- md_gov_18 |>
 inner_join(md_gov_county, by=c("GEOID", "County"))

#Add Columns to Generate Percentage for Cox and Hogan
md_cands_18_22 <- md_cands_18_22 |>
  mutate(total_votes_18 = Hogan+Jealous+Quinn+Schlakman+`Write-ins.x`)|>
  mutate(total_votes_22 = Cox+Moore+Lashar+Wallace+Harding+Sefcik+`Write-ins.y`)|>
  mutate(pct_cox = (Cox/total_votes_22)*100)|>
  mutate(pct_hogan = (Hogan/total_votes_18)*100)

#Export using write_csv
write_csv(md_cands_18_22, "data/md_county_votes.csv")
```

**Q2.** You're interested in seeing how the methods of voting have
changed in Maryland since 2018. Using the `md_votes_by_type.csv` that
has data from the top of the ticket (governor in 2018 and 2022,
president in 2020), make a chart showing the percentage of votes cast in
each category - early voting, election day and mail - over the three
years. You'll need to make those percentages in R and then export the
CSV using `write_csv`, then make the chart in Datawrapper. Have a title,
description and source that tells readers about the data. The title and
description should highlight the most newsworthy or important aspect.

HINT: In Datawrapper's "Check and Describe" tab, you can click on a
column to get the option of "hiding" it in any visualization.

What do you think the story here is? Put the answer below along with the
URL of your chart.

<https://www.datawrapper.de/_/TiBuy/>

The story here is that mail-in voting became much more popular during
the pandemic but the rates of voting in-person on election day became
more common after the pandemic ended. Still, mail-in voting remained
more common than pre-pandemic levels.

**A2.**

```{r}
#Load datasets
md_vote_types <- read_csv("data/md_votes_by_type.csv")|>
clean_names() 

#Make Percentages
#percent early
md_vote_types <- md_vote_types |>
  mutate(pct_early = (early/total)*100)
#percent election

md_vote_types <- md_vote_types |>
  mutate(pct_election = (election_day/total)*100)
#percent mail
  md_vote_types <- md_vote_types |>
  mutate(pct_mail = (mail/total)*100)
  
  #Export using write_csv
write_csv(md_vote_types, "data/md_vote_types.csv")
```

**Q3.** You want to know more about the geography of 911 overdose calls
in Montgomery County, Maryland, in 2022. To do that, you'll make a
choropleth map in Datawrapper. You will need to:

-   Read the file into R and create columns for the number of calls in
    each zip code and the percentage of all calls that number represents
    and then export that CSV to use in your map.
-   Search for Maryland zip codes (use the 2020 data) as the base map.
-   Upload the CSV file.
-   Change the tooltip to show both the number and the percentage (you
    can put them side by side or put one under the other). Make sure to
    properly format both numbers to make them readable.
-   Add labels to your map that locate prominent places in the county.
-   Have a title, description and source that tells readers about the
    data. The title and description should highlight the most newsworthy
    or important aspect.
-   Make any other changes to data that helps you make a more accurate
    map.

What do you think the story here is, and what would you want to know
more about? Put the answer below along with the URL of your map.

<https://www.datawrapper.de/_/20F6Y/>

The majority of calls took place in the center of the county whereas the
Northeastern part of Montgomery County had less than 1% of calls in each
zip code. It would be important to look at what is in the different zip
codes and the population make-up of them as well.

**A3.**

```{r}
#Load datasets
moco_overdose_calls <- read_csv("data/montgomery_2022_overdoses.csv")
#Calls by Zipcodes
calls_by_zip <- moco_overdose_calls |>
  group_by(zip) |>
  summarise(total_calls = n())

#Pct of total
calls_by_zip <- calls_by_zip  |>
  mutate(pct_total = (total_calls/659)*100)

 #Export using write_csv
write_csv(calls_by_zip, "data/calls_by_zip.csv")

```
